### 2015-06-17 reports/paper/introduction.tex
thesis update

Global Positioning System (GPS) is the prevailing technology used for outdoor localization. A set of 32 satellites equipped with synchronized atomic clock orbit around the earth and broadcast their time and position information at fixed intervals. A GPS receiver listens to at least 4 satellites and use their broadcasted timing information to infer the location. Commercial grade GPS has an average error of a few meters, depending on the size and quality of the receiver~\cite{intro:gps}. While accuracy in this range is good for many applications including driving navigation and vehicle tracking, it does not provide enough precision for local movement tracking. Ultrasound based indoor localization approaches on the other hand, have achieved sub-centimeter accuracy~\cite{intro:ultra}. However, ultrasound systems require the use of expensive transducers.

Bluetooth and Wi-Fi based technologies have gained popularity in indoor positioning recently, mainly due to the widespread deployment of bluetooth tags and Wi-Fi stations in public spaces. In these systems, signal strength received from different base stations are used for the estimation of the device location. However, their reported accuracy are in the range of $1$ to $5$ meters~\cite{intro:blue, intro:loc}, which is not enough for local movement tracking.

>>>>

Global Positioning System (GPS) is the prevailing technology used for outdoor localization. A set of 32 satellites equipped with synchronized atomic clock orbit around the earth and broadcast their time and position information at fixed intervals. A GPS receiver listens to at least 4 satellites and uses the broadcasted timing information to infer the location. Commercial grade GPS has an average error of a few meters, depending on the size and quality of the receiver~\cite{intro:gps}. While accuracy in this range is good for many applications including driving navigation and vehicle tracking, it does not provide enough precision for local movement tracking.

Ultrasound based indoor localization approaches, on the other hand, have achieved sub-centimeter accuracy~\cite{intro:ultra}. These systems employ multiple ultrasound receivers and use the arrival time difference between the sound source and receivers to infer the source location. Although obtaining good accuracy, ultrasound systems require the use of expensive transducers.

Bluetooth and Wi-Fi based technologies have gained popularity in indoor positioning recently, mainly due to the widespread deployment of bluetooth tags and Wi-Fi stations in public spaces. The fact that modern consumer devices such as mobile phones and tablets are commonly equipped with Wi-Fi and bluetooth modules also made this approach particular attractive because no hardware needs to be installed on the user end. Recent applications including serving advertisements and coupons to consumers in shopping centers based on the customer's location. In these systems, signal strength received from different base stations are used for the estimation of the device location. However, their reported accuracy are in the range of $1$ to $5$ meters~\cite{intro:blue, intro:loc}, which is not enough for local movement tracking.
